---
title: "2021-Project-1-Blog-Post"
author: "Alex Prevatte"
date: "10/7/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=TRUE,eval=FALSE}
rmarkdown::render("~/NCSU/ST558/Repos/aprevatte.github.io/_Rmd/2021-Project-1-Blog-Post.Rmd", 
              output_format = "github_document", 
              output_dir = "~/NCSU/ST558/Repos/aprevatte.github.io/_posts/",
              output_options = list(
                html_preview = FALSE
                )
              )
```

## Project 1 Findings 


This project [COVID-19](https://aprevatte.github.io/COVID19-API/) involved utilizing the COVID-19 API to construct contingency tables, summary statistics, and data visualizations for countries with the highest COVID-19 case count. I spent time writing functions that created dataframes for users to easily see the confirmed cases and deaths for a given region at any time. I then wanted to take a closer look at the daily confirmed case count, instead of focusing on the cumulative sum of cases which was provided in the API. This to me was important because I wanted to understand the rate of growth or decline of cases over time.

After conducting exploratory data analysis, I thought it was interesting that India, the second largest country by confirmed case count, had less deaths than Brazil, the third largest country by case count. I also found it interesting that the 'recovered' cases were 0 for every country over time, which makes me believe that the data either wasn't available or there was an error in data collection. I was hoping to prepare a report that displayed both COVID deaths and recoveries, but I ended up changing my functions since there was not data for recoveries in the summary endpoint. 

The most difficult part of the programming was connecting with the COVID-19 API and creating functions that worked for me. I have experience generating summaries, plotting, etc. but I didn't have a whole lot of experience coming into this project with connecting to APIs. After spending a fair amount of time on this project, I feel much more comfortable extracting data from APIs and would enjoy doing it again with other types of data. 

If I were to approach a similar project again, I would spend time writing out a plan of action for how I want to go about the analysis. I went into this project actually wanting to use a different API, but after reading the prompt more thoroughly, I had changed my mind. It's important to know that the direction you think that you are going in may change after taking a closer look at the data. I had originally wanted to incorporate the recoveries into my analysis, but I didn't have much data to work with so I decided against that route. I had a great experience working on this project and I see myself in the future wanting to performing my own data analysis on other APIs for my own interest.